\propertitle

### 2019-05-14 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-05-13T10:06:49+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation constraints%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample constraints}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Despite remarkable advances in recording technologies, the best
experimental measurements of neuronal activity can still only record a very
small sample of neurons compared to the number that constitutes a brain
area. Many probabilistic models focus on such samples only, somehow
neglecting, in their assumptions, that the recorded neurons are a sample
from a larger network. This kind of isolation assumptions sometimes escape
attention, being subtly hidden in the mathematics. Some probabilistic
models try to take also  unrecorded neurons into account, but
become very complex in doing so.

@@

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-05-13T11:41:45+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation constraints%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample constraints}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Despite remarkable advances in recording technologies, the best
experimental measurements of neuronal activity can still only record a very
small sample of neurons compared to the number that constitutes a brain
region. Many probabilistic models focus on such samples only, somehow
neglecting, in their assumptions, that the recorded neurons are a sample
from a larger network. This kind of isolation assumptions sometimes escape
attention, being subtly hidden in the mathematics. Some probabilistic
models try to take also unrecorded neurons into account, but become very
complex in doing so.

@@

The maximum-entropy method\mynote{refs} has been used for a variety of
inferences about neuronal activity from various brain areas and about other
phenomena of importance to the neurosciences, for example gene regulation
and protein sequencing\mynote{what's this exactly? refs}. This method is
often used to test whether some statistics of the data, for example
second-order time correlatins, is sufficient for making other inferences
about the data. It can be considered as an approximation of probabilistic
models based on various assumptions of inferential
sufficiency\mynote{refs} -- for example of empirical moments or of long-run
frequencies.

\mynote{Say something more about advantages of such question/answer: for
  example we can make statements about total activity of brain region even
  across recordings when sampled neurons aren't the same.}
